Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-05-24 meta_analysis_sexual_selection_pop_fitness.Rmd
Luke brms changes

**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
# Load the data and clean up the variable formats
prelim.data <- read.csv('data/Preliminary data frame 22.2.18.csv')
prelim.data$Study.ID <- prelim.data$Study.ID %>% factor()
prelim.data$Taxon <- prelim.data$Taxon %>% factor()
prelim.data$Group.ID <- prelim.data$Group.ID %>% factor()
prelim.data$Authors <- prelim.data$Authors %>% factor()
prelim.data$Environment <- prelim.data$Environment %>% factor %>% relevel(ref="Unstressed")
prelim.data$Sex <- prelim.data$Sex %>% factor %>% relevel(ref="B")
prelim.data$Ambiguous <- prelim.data$Ambiguous %>% factor()
prelim.data$Species <- prelim.data$Species %>% factor()
#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% factor() %>% relevel(ref="NO")
prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor() %>% relevel(ref="0")
prelim.data$Post.cop <- prelim.data$Post.cop %>% factor() %>% relevel(ref="0")
prelim.data$Blinding <- prelim.data$Blinding %>% factor()

@@

Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)

```
<br></br>

@@

<input type=button class=hideshow></input>
```{r}
model.preliminary <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + Generations + Blinding, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = prelim.data)

summary(model.preliminary)
```
<br></br>

@@

# Make sure the factors are leveled in the same order as we write our prediction function (below)
restricted.data$Environment <- restricted.data$Environment %>% factor() %>% relevel(ref="Unstressed")
restricted.data$Sex <- restricted.data$Sex %>% factor() %>% relevel(ref="M")
restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Beetle")

@@

summary(model.complete) 
```

>>>>

**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
# Load the data and clean up the variable formats
prelim.data <- read.csv('data/Preliminary data frame 22.2.18.csv')
prelim.data$Study.ID <- prelim.data$Study.ID %>% factor()
prelim.data$Group.ID <- prelim.data$Group.ID %>% factor()
prelim.data$Environment <- prelim.data$Environment %>% relevel(ref="Unstressed")
prelim.data$Sex <- prelim.data$Sex %>% relevel(ref="B")

#Outcome.Class.2 is using the categories that were decided by survey. I am keeping both just to check them against each other (how much of a difference it makes)
prelim.data$Outcome.Class <- prelim.data$Outcome.Class %>% relevel(ref="Indirect")
prelim.data$Enforced.Monogamy <- prelim.data$Enforced.Monogamy %>% relevel(ref="NO")
prelim.data$Pre.cop <- prelim.data$Pre.cop %>% factor() %>% relevel(ref="0")
prelim.data$Post.cop <- prelim.data$Post.cop %>% factor() %>% relevel(ref="0")
prelim.data$Blinding <- prelim.data$Blinding %>% factor()

@@

Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)
```
<br></br>

@@

<input type=button class=hideshow></input>
```{r}
model.preliminary <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + log(Generations) + Blinding, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = prelim.data)

summary(model.preliminary)

brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding 
                + (1|Study.ID) #group level effect #1
                + (1|Outcome)
                + (1|Taxon), 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.99, max_treedepth = 15),
                data = prelim.data %>% mutate(SE = sqrt(var.g)))

bayesplot::mcmc_areas(posterior_samples(brms.preliminary)[,1:11]) + geom_vline(xintercept = 0, linetype = 2)

new.data <- prelim.data %>% 
  mutate(SE = sqrt(var.g)) %>% 
  select(Sex, Environment, Blinding, Generations, SE) %>% 
  mutate(Generations = mean(log(Generations)), Blinding = "Blind", SE = 0) %>% 
  distinct() %>% arrange(Sex, Environment)
predictions <- data.frame(new.data, predict(brms.preliminary, newdata = new.data, re_formula = NA))

pd <- position_dodge(0.2)
predictions %>% ggplot(aes(Sex, Estimate, group = Environment)) + 
  geom_errorbar(aes(ymin = X2.5.ile, ymax = X97.5.ile), position = pd, width = 0) +
  geom_point(position = pd) +
  coord_flip()
```
<br></br>

@@

# Make sure the factors are leveled in the same order as we write our prediction function (below)
restricted.data$Environment <- restricted.data$Environment %>% factor() %>% relevel(ref="Unstressed")
restricted.data$Sex <- restricted.data$Sex %>% factor() %>% relevel(ref="M")
restricted.data$Outcome.Class <- restricted.data$Outcome.Class %>% factor() %>% relevel(ref="Indirect")
restricted.data$Taxon <- relevel(restricted.data$Taxon, ref = "Beetle") 
restricted.data$Outcome <- restricted.data$Outcome %>% factor()

@@

summary(model.complete)

brms.complete <- brm(g | se(SE)  ~ 1 + Sex * Environment + Taxon + Outcome
                + (1|Study.ID), #group level effect #1
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = restricted.data %>% mutate(SE = sqrt(var.g)))

brms.complete2 <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding + 
                + (1|Taxon) #group level effect #1
                + (1|Outcome) #group level effect #1
                + (1|Study.ID), #group level effect #1
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.9999, max_treedepth = 15),
                data = restricted.data %>% mutate(SE = sqrt(var.g)))

bayesplot::mcmc_areas(posterior_samples(brms.complete)[,1:24]) + geom_vline(xintercept = 0, linetype = 2)
bayesplot::mcmc_areas(posterior_samples(brms.complete2) %>% select(-starts_with("r"), -lp__)) + geom_vline(xintercept = 0, linetype = 2)

post <- (posterior_samples(brms.complete, 
                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
                                    "b_SexF:EnvironmentStressed", "b_OutcomeReproductiveSuccess")) %>%
  mutate(both_benign = b_Intercept + b_SexB + b_OutcomeReproductiveSuccess,
         both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed` + b_OutcomeReproductiveSuccess,
         male_benign = b_Intercept + b_OutcomeReproductiveSuccess,
         male_stressful = b_Intercept + b_EnvironmentStressed + b_OutcomeReproductiveSuccess,
         female_benign = b_Intercept + b_SexF + b_OutcomeReproductiveSuccess,
         female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed` + b_OutcomeReproductiveSuccess))[,-(1:7)]

post2 <- (posterior_samples(brms.complete, 
                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
                                    "b_SexF:EnvironmentStressed")) %>%
  mutate(both_benign = b_Intercept + b_SexB,
         both_stressful = b_Intercept + b_SexB + `b_SexB:EnvironmentStressed`,
         male_benign = b_Intercept,
         male_stressful = b_Intercept + b_EnvironmentStressed ,
         female_benign = b_Intercept + b_SexF ,
         female_stressful = b_Intercept + b_SexF + `b_SexF:EnvironmentStressed` ))[,-(1:6)]

bayesplot::mcmc_areas(post) + geom_vline(xintercept = 0, linetype = 2)

new.data <- restricted.data %>% 
  mutate(SE = sqrt(var.g)) %>% 
  select(Sex, Environment, Blinding, Generations, SE, Taxon) %>% 
  mutate(Generations = mean(log(Generations)), 
         Blinding = "Blind", 
         Taxon = "Fly",
         Outcome = "Reproductive Success",
         SE = 0) %>% 
  distinct() %>% arrange(Sex, Environment)
predictions.complete <- data.frame(new.data, fitted(brms.complete, newdata = new.data, re_formula = NA))

pd <- position_dodge(0.2)
predictions.complete %>% ggplot(aes(Sex, Estimate, group = Environment, colour = Environment)) + 
  geom_errorbar(aes(ymin = X2.5.ile, ymax = X97.5.ile), position = pd, width = 0) +
  geom_point(position = pd) +
  coord_flip()
```
